The Morality of Arbitrage

### 2017-05-22 Draft/draft2.Rmd
Update draft2.Rmd

@@

>>>>

The dictionary definition of a Dutch book is the following:

"A principle for dynamic decision-making situations that leads to a sequence of bets finishing in an inescapable loss, as in the case of a bookmaker always gaining from gambling on the outcome of horse races."[^1].

@@

[^1]: See the Routledge Dictionary of Economics entry on "Dutch books."
